Paradigms in Physics 2.0

### 2017-06-07 paper.tex
work on text

\subsection{Background}
\emph{What is the Paradigms now?}
\subsection{History of the Paradigms}
\emph{How did we get here?~\cite{manogue2001paradigms}}
\subsection{Motivation for the change}
\emph{Why change? Why now? Should you do the same?}

@@

@@

\section{Tables and Figures}

Figures, tables, and equations must be inserted in the text and may
not be grouped at the end of the paper. Important: miscounting of
figures, tables, or equations may result from revisions. Please double
check the numbering of these elements before you submit your paper to
the volume editor.
% LaTeX handles this automatically via the \label and \ref commands.

\subsection{Figures}

If your manuscript contains figures, they are typically placed in one
column (see Fig.\ \ref{fig1}).  A large figure might span two columns
(see Fig.\ \ref{fig2}).  Cite all figures in the text
consecutively. The word ``Figure'' should be spelled out if it is the
first word of the sentence and abbreviated as ``Fig.'' elsewhere in
the text. Place the figures as close as possible to their first
mention in the text at the top or bottom of the page.

@@

\subsubsection{Color figures}
Beginning in 2013, color figures are allowable since the PERC
Proceedings will be available only in an online format.  However,
authors are encouraged to check that the figures print in black and
white without loss of clarity.

@@

% REVTeX provides a ruledtabular environment that automatically sizes tables, adds double 
% lines, and adjusts column spacing. Use it around the regular tabular environment.
% For a two-column table, use \begin{table*} instead (with matching \end{table*}.
\begin{table}[htbp]
\caption{This is a sample table.\label{tab1}}
\begin{ruledtabular}
\begin{tabular}{cl}
 & \textbf{MS Word} \\
 & \textbf{US Letter Size Paper} \\
 \hline
Primary Heading & Roman numerals, all capital letters \\
First subheading & Capital letters, only first \\
 & letter of first word capitalized \\
Second subheading & Numbers, italicized 
\end{tabular}
\end{ruledtabular}
\end{table}

%\newcommand\mathcourse[2]{\emph{#1 (#2)}}
\newcommand\mathcourse[2]{\emph{#1}}
\newcommand\noted[2]{\textbf{#1} (#2)}
\newcommand\paradigm[1]{#1 (3)}
\newcommand\capstone[1]{#1 (3)}
\newcommand\onecredit[1]{#1 (1)}
\newcommand\threecredit[1]{#1 (3)}
\newcommand\fourcredit[1]{#1 (4)}

\begin{table*}[htbp]
\caption{Hypothetical transfer student schedule.\label{schedule}}
\begin{ruledtabular}
\begin{tabular}{rlll}
  \textbf{Year} & \textbf{Fall} & \textbf{Winter} & \textbf{Spring} \\
  \hline
3 & \paradigm{Quantum fundamentals} & \paradigm{Osciallations and waves} & \paradigm{Static fields}
\\
  & \paradigm{Energy and entropy} & \paradigm{Periodic systems} & \paradigm{Central forces}
\\
  & \onecredit{Computational lab I} & \onecredit{Computational lab II} & \onecredit{Computational lab III}
\\
  & \threecredit{Electronics} & \threecredit{Computer interfacing} & \onecredit{Research}
\\
&& \noted{Challenges}{3} & \noted{Theoretical Mechanics}{3}
\\
\hline 4 & \capstone{Electromagnetism capstone} & \capstone{Quantum capstone} & \capstone{Thermal capstone}
\\
& \onecredit{Thesis} & \onecredit{Thesis} & \onecredit{Thesis}
\\
& \onecredit{Research} & \onecredit{Research}
\end{tabular}
\end{ruledtabular}
\end{table*}

@@

\section{Other issues}

\subsection{Copyright transfer}
All accepted papers will be made available under a Creative Commons Attribution 3.0 License (CC-BY).

\subsection{Citations}
When you are preparing references, please use the PRST--PER Style
Guide~\cite{style-guide}.  This document contains information about
how references should be formatted, including proper journal
abbreviations.  Examples directly from that style guide of a journal,
book, proceedings paper, and dissertation are also provided
here~\cite{smith-brown,smith,smith-proc,smith-diss}.

\subsection{Permissions}
To use previously published material from a book or journal, you must
obtain written permission from the owner of the rights to the material
(the original publisher and/or author). It is your responsibility to
obtain permission to use copyrighted material. The executed
permissions need to be sent along with the manuscript to your volume
editor. Most publishers offer submission of permission requests online
or via email, which may be the fastest and most convenient way of
receiving a reply. Some examples with relevant links are:

\begin{itemize}
\item \url{http://www.elsevier.com/locate/permissions}
\item \url{http://www.ieee.org}
\item \url{http://www.nature.com}
\item \url{http://www.sciencemag.org}
\end{itemize}

You may also use the Permission Request Form to request permission to
reprint text, tables or figures. You may complete this form and fax it
to the publisher or author of the material you wish to use. A blank
form is available for download click on Forms. When the signed
permission is returned to you, please insert any necessary credit
lines in your figure or table legends.

>>>>

\subsection{Background}
\emph{What is the Paradigms now?}
\subsection{History of the Paradigms}
\emph{How did we get here?~\cite{manogue2001paradigms}}
\subsection{Motivation for the change}
\paragraph{Curricular changes}
There were a number of factors that motivated us to embark on the
Paradigms~2.0 process.  The original Paradigms in Physics curricular
reform from 200? was showing its age.  In the intervening years we had
made a large number of modifications, such as reordering Paradigms,
introducing one new Paradigm, and introducing and changing
computational physics courses.  However, there were other changes
needed that could not be separated from an examination of the
curriculum as a whole.  Most notable were discussions of the
requirements for computational physics, the amount of required
electronics credits, and the role of our modern physics course.  These
persistent issues were not easily addressed without addressing the
physics major curriculum as a whole.

\paragraph{New faculty}
At this stage, (XX) of our faculty was not present during the orignal
Paradigms effort.  Many of the newer faculty have only a superficial
undertanding of our course structure.  This poses a challenge when
these professors teach courses that are closely intertwined with one
another.

@@

%\newcommand\mathcourse[2]{\emph{#1 (#2)}}
\newcommand\mathcourse[2]{\emph{#1}}
\newcommand\noted[2]{\textbf{#1} (#2)}
\newcommand\paradigm[1]{{\sc #1} (3)}
\newcommand\capstone[1]{#1 (3)}
\newcommand\onecredit[1]{#1 (1)}
\newcommand\threecredit[1]{#1 (3)}
\newcommand\fourcredit[1]{#1 (4)}

\begin{table*}[htbp]
\caption{Hypothetical transfer student schedule.  Most transfer
  students will have a heavier schedule in their transfer year due
  to need to catch up on required math courses.\label{schedule}}
\begin{ruledtabular}
\begin{tabular}{rlll}
  \textbf{Year} & \textbf{Fall} & \textbf{Winter} & \textbf{Spring} \\
  \hline
3 & \paradigm{Quantum fundamentals} & \paradigm{Osciallations and waves} & \paradigm{Static fields}
\\
  & \paradigm{Energy and entropy} & \paradigm{Periodic systems} & \paradigm{Central forces}
\\
  & \onecredit{Computational lab I} & \onecredit{Computational lab II} & \onecredit{Computational lab III}
\\
  & \threecredit{Electronics} & \threecredit{Computer interfacing} & \onecredit{Research}
\\
& \mathcourse{Linear algebra}{341} & \noted{Challenges}{3} & \noted{Theoretical Mechanics}{3}
\\
&&\mathcourse{Vector calculus}{255}
\\
\hline 4 & \capstone{Electromagnetism capstone} & \capstone{Quantum capstone} & \capstone{Thermal capstone}
\\
& \onecredit{Thesis} & \onecredit{Thesis} & \onecredit{Thesis}
\\
& \onecredit{Research} & \onecredit{Research}
\end{tabular}
\end{ruledtabular}
\end{table*}

@@

@@

@@

@@
